### 2009-02-26 docs/spherical_basestate/basestate.tex
addressed some marginpars, put in section labels with proper referencing in the flowchart
updated correct base description

\subsection{Calculation of $w_0$}

@@

\subsection{{\bf Advect Base}}

@@

\subsection{Correct Base}

The base state density correction now includes the area factors in the divergences,
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp}  - \frac{1}{r_j^2} \frac{\dt}{\dr} \left [ \left(r^2 \etarho\right)_{j+\myhalf} - \left(r^2 \etarho\right)_{j-\myhalf} \right ] \enskip .
\end{equation}

>>>>

\subsection{Calculation of $w_0$}\label{Sec:Spherical w0 Calculation}

@@

\subsection{{\bf Advect Base}}\label{Sec:Advect Base Spherical}

@@

\subsection{\bf{Correct Base}}

The is the process by which we adjust the base state density to account for
large-scale mixing.  It can also be used to adjust the base state enthalpy
to account for large-scale mixing, reactions, and thermal diffusion.
We have simplified the algorithm greatly by simply setting $\nabla\cdot\etarho$
equal to the averaged difference between the base state and full state.

\begin{equation}
\rho_0^{\outp} = \rho_0^{\inp} + \underbrace{{\rm{\bf Avg}}(\rho^{\inp} - \rho_0^{\inp})}_{-\Delta t\nabla\cdot\etarho}.
\end{equation}
